\input opustex
\input opusgreg

\input eplain

\font\bigtype = hmin10 scaled \magstep2
\font\Bigtype = hmin17 scaled \magstep2

\font\musicaps = Priory scaled \magstep5
\font\textcaps = Priory scaled \magstep4

\musicinitialfont\musicaps
\textinitialfont\textcaps

\special{papersize=148mm,210mm}

\hoffset1.5mm
\voffset-7mm
\hsize100mm
\vsize173mm

\def\beginhymn #1.{\centerline{\bigtype {#1}}\par\bigskip}

\def\mycr{\par\vskip-\parskip}

\def\beginlyrics{\begingroup
                       \def\\{\mycr}
                       \pretolerance=10000
                       \raggedright
                       \parskip=5pt
                       \parindent-3mm}
\def\endlyrics{\endgroup}

\def\verse#1. {\hskip2mm\llap{{\oldstyle #1}. }}

\font\smallrm = cmr8
\font\smold = cmmi10 scaled 900

\def\source#1\par{\rightline{\smallrm #1}}


\nopagenumbers

\beginhymn O Sacred Head sore wounded.

\moveleft0mm\hbox{

\vtop{
\hsize55mm
{\leftskip1em
\textinitial{O}{ Sacred Head!} sore wounded,\\}
\beginlyrics
\qquad With grief and shame weighed down,\\
O Kingly Head! surrounded\\
\quad With thorns, thy only crown;\\
Death's pallor now comes o'er thee,\\
\quad The glow of life decays,\\
Yet hosts of heaven adore thee\\
\quad And tremble as they gaze.

\verse2. What language shall I borrow\\
\quad To thank thee, dearest Friend,\\
For this thy dying sorrow,\\
\quad Thy pity without end?\\
O agony and dying!\\
\quad O love to sinners free!\\
Jesus, all grace supplying,\\
\quad Turn thou thy face on me.

\endlyrics

}

\hskip3mm

\vtop{
\hsize50mm

\beginlyrics

\verse3. In this thy bitter passion\\
\quad Sweet Jesus, think of me.\\
With thy most sweet compassion,\\
\quad Unworthy though I be:\\
Beneath thy cross abiding\\
\quad Forever would I rest,\\
In thy dear love confiding,\\
\quad And with thy presence blest.

\verse4. Be thou my consolation,\\
\quad My shield, when I must die;\\
Remind me of thy passion\\
\quad When my last hour draws nigh.\\
Mine eyes shall then behold thee;\\
\quad Upon thy cross shall dwell,\\
My heart by faith enfold thee;\\
\quad Who dieth thus, dies well.

\endlyrics

}
}

\medskip

\source Paul Gerhardt {\smold 1607}-{\smold 76} from Salve caput cruentatum

\source attrib. Bernard of Clairvaux

\source tr. Henry Williams Baker {\smold 1821}-{\smold 77} and

\source James Waddell Alexander {\smold 1804}-{\smold 59}

\end