% This file was converted to LaTeX by Writer2LaTeX ver. 1.4
% see http://writer2latex.sourceforge.net for more info
\documentclass[a5paper]{article}
%\usepackage[ascii]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{libertine}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\newfontfamily\jarman{JARDOTTY}
\usepackage{color}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,nohead,nofoot]{geometry}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}
% Footnote rule
\setlength{\skip\footins}{0.119cm}
\renewcommand\footnoterule{\vspace*{-0.018cm}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.018cm}}\vspace*{0.101cm}}

\newcommand\textjarman[1]{{\jarman #1}}
\newcommand\answer[1]{\textbf{\textit{#1}}}
\newcounter{z}
\setcounter{z}{0}
\newcommand\spaces[1]{ \_\loop \ifnum\value{z} < #1
~\_%
\stepcounter{z}%
\repeat%
\setcounter{z}{0}}

\title{}
\begin{document}

\setlength{\parskip}{6pt plus2pt minus2pt}


\noindent Name:

\noindent {\Large Chapter XLV -- Confirmation}

1. Confirmation gives us light and \spaces{7} to be worthy \spaces{7}  of  Christ, 

2.
He instituted it by (\textjarman{administering}) (\textjarman{promising}) it.

3. In it we receive  the
\spaces{7} as the Apostles did at Pentecost.

4. Scripture  often  speaks  of  the
Apostles imposing hands on persons already baptised,  and  giving  them  the
\spaces{7}.

5. By baptism  we  are  \spaces{7}  in  the  supernatural  order;  but  by
confirmation we are true \spaces{7}.

6. The Sign  Only  of  confirmation  is  the
\spaces{7}; the Thing and the Sign is the \spaces{7}; the Thing Only is the \spaces{7}. 

7.
The remote matter is \spaces{7}, which is made up of  \spaces{7}  and  \spaces{7},  and  is
blessed by \spaces{7}.

8. The proximate matter is \spaces{7}.

9. The  form  is  \spaces{7}.

10. The subject of confirmation  is  \spaces{7}. 

11.  The  immediate  effect  of
confirmation is \spaces{7}.

12. The ultimate effect is \spaces{7}.

13.  The  character
given makes us like to Christ in His (\textjarman{private}) (\textjarman{public}) life.

14.  It  gives
us (\textjarman{at the moment of reception only}) (\textjarman{all through life}) a  right  to  graces
necessary to profess, live and defend our \spaces{7}.

15. It gives  or  increases
in us the seven Gifts of  the  \spaces{7}. 

16.  In  martyrdom,  it  enables  the
recipient to act as (\textjarman{principal}) (\textjarman{instrumental}) cause  of  the  steadfastness
required.

17. It is through the character given by (\textjarman{baptism})  (\textjarman{confirmation})
(\textjarman{Holy Orders}) that Christ provides for His Church in every  century  members
who are  willing  to  fight  and  die  for  the  faith. 

18.  The  character
(\textjarman{disappears}) (\textjarman{does not disappear}) as soon as the chrism disappears from  our
forehead.

19. An adult and especially a soldier should be  characterised  by
breadth of \spaces{7}, a sense of \spaces{7},  and  action  for  the  \spaces{7}. 

20.  The
following Popes have strongly advocated Catholic  Action  in  recent  times:
\spaces{7}, \spaces{7}, \spaces{7} and \spaces{7}.

21. Pius XI describes Catholic Action  as  “A
participation of the  \spaces{7}  in  the  \spaces{7}  of  the  Church's  \spaces{7}.” 

22.
Catholic Action is based on (\textjarman{love}) (\textjarman{hatred}); atheistic  communism  is  based
on (\textjarman{love}) (\textjarman{hatred}).

23. In practising Catholic Action I must obey  the  Pope
and the \spaces{7}.

24. Here  are  five  things  I  must  do  if  I  want  to  be
successful as a Catholic Actionist: I must
\begin{enumerate}
\item \spaces{7}
\item \spaces{7}
\item \spaces{7}
\item \spaces{7}
\item \spaces{7}
\end{enumerate}


25. If I live and fight for Christ on earth, I shall reign  with  Him
in \spaces{7}.

\newpage

1. Confirmation gives us light and \answer{strength} to be worthy \answer{soldiers}  of  Christ, 
2.
He instituted it by (administering) \answer{(promising)} it.
3. In it we receive  the
\answer{Holy Ghost} as the Apostles did at Pentecost.
4. Scripture  often  speaks  of  the
Apostles imposing hands on persons already baptised,  and  giving  them  the
\answer{Holy Ghost}.
5. By baptism  we  are  \answer{born}  in  the  supernatural  order;  but  by
confirmation we are true \answer{adults}.
6. The Sign  Only  of  confirmation  is  the
\answer{external ceremony}; the Thing and the Sign is the \answer{character}; the Thing Only is the \answer{grace given}. 
7.
The remote matter is \answer{chrism}, which is made up of  \answer{olive oil}  and  \answer{balm},  and  is
blessed by \answer{the Bishop}.
8. The proximate matter is \answer{the imposition of hands and the anointing}.
9. The  form  is  \answer{I sign thee with the sign of the Cross, and I confirm thee with the chrism of salvation, in the name of the Father, and of the Son, and of the Holy Ghost.}.
10. The subject of confirmation  is  \answer{a baptized person}. 
11.  The  immediate  effect  of
confirmation is \answer{the character}.
12. The ultimate effect is \answer{light and strength and Gifts of the Holy Ghost}.
13.  The  character
given makes us like to Christ in His (private) (\answer{public}) life.
14.  It  gives
us (at the moment of reception only) (\answer{all through life}) a  right  to  graces
necessary to profess, live and defend our \answer{faith}.
15. It gives  or  increases
in us the seven Gifts of  the  \answer{Holy Ghost}. 
16.  In  martyrdom,  it  enables  the
recipient to act as (principal) (\answer{instrumental}) cause  of  the  steadfastness
required.
17. It is through the character given by (baptism)  (\answer{confirmation})
(Holy Orders) that Christ provides for His Church in every  century  members
who are  willing  to  fight  and  die  for  the  faith. 
18.  The  character
(disappears) (\answer{does not disappear}) as soon as the chrism disappears from  our
forehead.
19. An adult and especially a soldier should be  characterised  by
breadth of \answer{outlook}, a sense of \answer{responsibility},  and  action  for  the  \answer{common good}. 
20.  The
following Popes have strongly advocated Catholic  Action  in  recent  times:
\answer{Leo XIII}, \answer{Pius X}, \answer{Pius XI} and \answer{Pius XII}.
21. Pius XI describes Catholic Action  as  “A
participation of the  \answer{laity}  in  the  \answer{apostolate}  of  the  Church's  \answer{hierarchy}.” 
22.
Catholic Action is based on (\answer{love}) (hatred); atheistic  communism  is  based
on (love) (\answer{hatred}).
23. In practising Catholic Action I must obey  the  Pope
and the \answer{bishops}.
24. Here  are  five  things  I  must  do  if  I  want  to  be
successful as a Catholic Actionist: I must \answer{understand my faith better daily}, \answer{love the faith wholeheartedly},  \answer{train to argue with sympathy and insight},  \answer{follow the ruling of the Church}  and
\answer{put  ourselves in God's hands}. (extra answer: \answer{increase in supernatural charity})
25. If I live and fight for Christ on earth, I shall reign  with  Him
in \answer{heaven}.

\end{document}
