% This file was converted to LaTeX by Writer2LaTeX ver. 1.4
% see http://writer2latex.sourceforge.net for more info
\documentclass[a4paper,14pt]{memoir}
%\usepackage[ascii]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{libertine}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\newfontfamily\jarman{JARDOTTY}
\usepackage{color}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,nohead,nofoot]{geometry}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}
% Footnote rule
\setlength{\skip\footins}{0.119cm}
\renewcommand\footnoterule{\vspace*{-0.018cm}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.018cm}}\vspace*{0.101cm}}

\newcommand\textjarman[1]{{\jarman #1}}
\newcommand\answer[1]{\textbf{\textit{#1}}}
\newcounter{z}
\setcounter{z}{0}
\newcommand\spaces[1]{\rule{0pt}{18pt} \_\loop \ifnum\value{z} < #1
~\_%
\stepcounter{z}%
\repeat%
\setcounter{z}{0}}

\title{}
\begin{document}

\setlength{\parskip}{6pt plus2pt minus2pt}


\noindent Name:

\noindent {\Large Chapter LIII -- Purgatory}



1. Four effects of formal sin are \spaces{7}, \spaces{7}, \spaces{7}, \spaces{7}.  

2.  Guilt
is  abolished  by  \spaces{7},  and  \spaces{7}.  

3.  It  is  abolished  (\textjarman{partially})
(\textjarman{wholly}). 

4. The forgiving of sin  (\textjarman{does})  (\textjarman{does  not})  necessarily  abolish
also all temporal punishment due to sin. 

5. The guilt of venial sin and  all
evil inclinations and habits due to  sin  are  abolished  at  death  by  the
fervour of the soul's \spaces{7}. 

6. Any \spaces{7} due to  sin,  however,  remains,


7. This (\textjarman{can}) (\textjarman{cannot}) keep a soul  from  entering  heaven  immediately. 

8. 
Purgatory is a \spaces{7} and a \spaces{7} in which the souls of  persons  who  have
died in \spaces{7} suffer on account of the \spaces{7} due to sins  committed  after
\spaces{7}, before they can be admitted into \spaces{7}. 

9. We know  that  purgatory
exists because \spaces{7} has told us that it does. 

10.  We  know  that  He  has
done this because \spaces{7} assures us infallibly  that  He  has.  

11.  It  was
\spaces{7} who sent gold and silver to Jerusalem to have sacrifice  offered  for
the dead. 

12. Scriptures approved of his action  when  it  said:  “It  is  a
\spaces{7} and \spaces{7} thought to pray for the \spaces{7} that they may  be  \spaces{7}.”


13. It was St. \spaces{7} who begged her son, Augustine, to have Mass  said  for
her soul after her death. 

14. At death most people are not  good  enough  to
go straight to \spaces{7}, nor bad enough  to  go  to  \spaces{7}.  This  shows  how
reasonable it is to believe in the existence of \spaces{7}.  

15.  The  doctrine
of purgatory brings home to us God's \spaces{7}, His  \spaces{7},  and  His  \spaces{7}.


16. The main suffering in purgatory is \spaces{7}. 

17. It consists in the  delay
of the \spaces{7}. 

18. It is an intense spiritual hunger  for  \spaces{7}.  

19.  The
Church (\textjarman{has}) (\textjarman{has not}) defined that there is  material  fire  in  purgatory.


20. There will be no purgatory after the  \spaces{7}.  

21.  Souls  in  purgatory
(\textjarman{do})  (\textjarman{do  not})  experience  great  joy.  

22.  They  (\textjarman{can})   (\textjarman{cannot})   help
themselves; they (\textjarman{can}) (\textjarman{cannot}) help  other  souls  there.  

23.  They  (\textjarman{can})
(\textjarman{cannot}) be helped by souls in heaven. 

24. We can help  them  most,  because
our good deeds entail \spaces{7}; hence, win (\textjarman{merit})  (\textjarman{satisfaction})  for  them.


25. We can help them by \spaces{7}, \spaces{7}, \spaces{7}, \spaces{7}, \spaces{7}, \spaces{7}. 

26. 
It (\textjarman{is}) (\textjarman{is not}) contrary to humility to wish to  avoid  purgatory.  

27.  We
can avoid it by 
\begin{itemize}
\item \spaces{7},
\item  \spaces{7},  
\item \spaces{7}, 
\item \spaces{7}, 
\item \spaces{7}.
\end{itemize} 

28. 
The Church on earth is called the Church \spaces{7}; the Church in purgatory  is
called the Church \spaces{7}; the Church in heaven is called the Church  \spaces{7};
 all form one organism called the \spaces{7} Body of Christ. 

29. The Heroic  Act
(\textjarman{is}) (\textjarman{is not}) a vow. 

30. If I  go  to  purgatory  I  shall  benefit  by  the
suffrages offered for me to the extent that I have been  devoted  to  \spaces{7}
while on earth.

\newpage


1. Four effects of formal sin are \answer{Guilt, a debt of punishment, evil inclinations, bad habits}
2.   Guilt
is  abolished  by  \answer{an act of perfect contrition}, \answer{the sacrament of penance}  and  \answer{martyrdom}. 
3.   It  is  abolished 
(\answer{wholly}).
4.  The forgiving of sin (\answer{does  not})  necessarily  abolish
also all temporal punishment due to sin.
5.  The guilt of venial sin and  all
evil inclinations and habits due to  sin  are  abolished  at  death  by  the
fervour of the soul's \answer{charity}.
6.  Any \answer{punishment} due to  sin,  however,  remains,
7. This (\answer{can}) keep a soul  from  entering  heaven  immediately. 
8. 
Purgatory is a \answer{place} and a \answer{state} in which the souls of  persons  who  have
died in \answer{grace} suffer on account of the \answer{temporal punishment} due to sins  committed  after
\answer{baptism}, before they can be admitted into \answer{heaven}.
9.  We know  that  purgatory
exists because \answer{Jesus Christ} has told us that it does.
10.   We  know  that  He  has
done this because \answer{the Church} assures us infallibly  that  He  has. 
11.   It  was
\answer{Judas Macchabeus} who sent gold and silver to Jerusalem to have sacrifice  offered  for
the dead.
12.  Scriptures approved of his action  when  it  said:  ``It  is  a
\answer{holy} and \answer{wholesome} thought to pray for the \answer{dead} that they may  be  \answer{loosed from their sins}.''
13. It was St. \answer{Monica} who begged her son, Augustine, to have Mass  said  for
her soul after her death.
14.  At death most people are not  good  enough  to
go straight to \answer{heaven}, nor bad enough  to  go  to  \answer{hell}.  This  shows  how
reasonable it is to believe in the existence of \answer{purgatory}. 
15.   The  doctrine
of purgatory brings home to us God's \answer{Sanctity}, His  \answer{Justice},  and  His  \answer{Mercy}.
16. The main suffering in purgatory is \answer{the pain of loss}.
17.  It consists in the  delay
of the \answer{Beatific Vision}.
18.  It is an intense spiritual hunger  for  \answer{God}. 
19.   The
Church (has) (\answer{has not}) defined that there is  material  fire  in  purgatory.
20. There will be no purgatory after the  \answer{Last Day}. 
21.   Souls  in  purgatory
(\answer{do})  (do  not)  experience  great  joy. 
22.   They  (can)   (\answer{cannot})   help
themselves; they (\answer{can}) (cannot) help  other  souls  there. 
23.   They  (\answer{can})
(cannot) be helped by souls in heaven.
24.  We can help  them  most,  because
our good deeds entail \answer{suffering}; hence, win (merit)  (\answer{satisfaction})  for  them.
25. We can help them by \answer{prayer}, \answer{good works}, \answer{sufferings}, \answer{the Mass}, \answer{Indulgences}, \answer{the Heroic Act}. 
26. 
It (is) (\answer{is not}) contrary to humility to wish to  avoid  purgatory. 
27.   We
can avoid it by \answer{Martyrdom. Baptism. Indulgences. The Mass. The Sacraments. The Religious Life. A spirit of penance. Sufferings.}
28. 
The Church on earth is called the Church \answer{militant}; the Church in purgatory  is
called the Church \answer{suffering}; the Church in heaven is called the Church  \answer{triumphant};
 all form one organism called the \answer{Mystical} Body of Christ.
29.  The Heroic  Act
(is) (\answer{is not}) a vow.
30.  If I  go  to  purgatory  I  shall  benefit  by  the
suffrages offered for me to the extent that I have been  devoted  to  \answer{the Holy Souls}
while on earth.

\end{document}
