% This file was converted to LaTeX by Writer2LaTeX ver. 1.4
% see http://writer2latex.sourceforge.net for more info
\documentclass[a4paper,14pt]{memoir}
%\usepackage[ascii]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{libertine}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\newfontfamily\jarman{JARDOTTY}
\usepackage{color}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,nohead,nofoot]{geometry}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}
% Footnote rule
\setlength{\skip\footins}{0.119cm}
\renewcommand\footnoterule{\vspace*{-0.018cm}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.018cm}}\vspace*{0.101cm}}

\newcommand\textjarman[1]{{\jarman #1}}
\newcommand\answer[1]{\textbf{\textit{#1}}}
\newcounter{z}
\setcounter{z}{0}
\newcommand\spaces[1]{\rule{0pt}{18pt} \_\loop \ifnum\value{z} < #1
~\_%
\stepcounter{z}%
\repeat%
\setcounter{z}{0}}

\title{}
\begin{document}

\setlength{\parskip}{6pt plus2pt minus2pt}


\noindent Name:

\noindent {\Large Chapter LIV -- Heaven and Hell}



1. Our Last end is to promote \spaces{5} \spaces{7} in  eternity.  

2.  We  shall  do  this
either in \spaces{7} or in \spaces{7} according to our choice. 

3. Man's first  great
need is \spaces{7}.  

4.  In  heaven  God's  essence  is  known  by  the  blessed
(\textjarman{mediately}) (\textjarman{immediately}). 

5. St. Paul says: “But then I shall know even  as
\spaces{2} \spaces{3} \spaces{7}.” 

6. St. John says that in heaven we shall see God “even as \spaces{3} \spaces{3}.”


7. Only by the help of the \spaces{7} \spaces{3} \spaces{7} will our intellect be able  to  stand  the
beatific vision. 

8. Man's second great need is \spaces{7}. 

9. The  blessed  know
and love God to the full extent to which He is knowable and lovable.  (\textjarman{True})
(\textjarman{False}). 

10. They know Him in the way He knows Himself, and  they  love  Him
in the way He loves Himself. (\textjarman{True}) (\textjarman{False}). 

11.  They  know  and  love  Him
infinitely. (\textjarman{True}) (\textjarman{False}). 

12. Sharing His knowledge and  love,  they  must
share also His \spaces{7}. 

13. A  being  is  perfectly  happy  when  it  has  no
desires \spaces{7} forever. 

14. All our desires for sensible  delights  will  be
fully satisfied in heaven  after the \spaces{7}.  

15.  The  beatific  vision  (\textjarman{can})
(\textjarman{cannot}) be lost by those in heaven. 

16. Heaven (\textjarman{is}) (\textjarman{is not})  eternal.  

17.
Some souls will be happier than others in heaven. (\textjarman{True})  (\textjarman{False}).  

18.  The
degree of happiness will depend on \spaces{7}. 

19. Christ will invite  even  the
least of the blessed to “enter the joy  of the \spaces{7}.”  

20.  Heaven  is  often
called “eternal \spaces{7}.” 

21. Hell was  first  made  to  punish  \spaces{7}.  

22.
Christ threatened with \spaces{7} those who refused to accept  His  truths.  

23.
On the Last Day, He will  say  to  the  lost:  “\spaces{7} \spaces{4} \spaces{3} \spaces{4} \spaces{7} \spaces{4}.”  

24.  This  is  the
sentence of  a  \spaces{7};  hence  its  words  must  be  taken  in  a  (\textjarman{proper})
(\textjarman{figurative}) sense. 

25. The main suffering in hell is the \spaces{7}. 

26. It  is
made up of  four  different  sufferings,  namely  \spaces{9},   \spaces{9},  \spaces{9},
\spaces{9}. 

27. Instead of hope, there is \spaces{7} in hell.  

28.  The  regret  of
the lost concerning sin is called \spaces{7}, it (\textjarman{is}) (\textjarman{is not}) true  contrition.


29. We (\textjarman{do}) (\textjarman{do not}) admit the presence of material fire in hell. 

30.  Every
material thing can enable a spirit to be in a \spaces{7}. 

31.  It  can  imprison
it there, if used as God's \spaces{8}. 

32. The Church (\textjarman{has})  (\textjarman{has  not})  defined
that hell is eternal. 

33. A soul in hell (\textjarman{would}) (\textjarman{would not}) come out if  it
were allowed to do so. 

34. In every mortal sin we choose  ourselves  instead
of God as our \spaces{4} \spaces{3}. 

35. As far as our natural power goes, this  choice  is
\spaces{9}. 

36. If we repent, it is due to \spaces{7}. 

37. God (\textjarman{can})  (\textjarman{cannot})  give
the grace of repentance to a soul in hell. 

38. Every  human  being  must  be
happy in eternity unless he deliberately chooses  to  be  otherwise.  (\textjarman{True})
(\textjarman{False}). 

39. No one can go to hell except  through  his  own  fault.  (\textjarman{True})
(\textjarman{False}). 

40. Christ says: “What doth it profit a man if he gain \spaces{7},  and
suffer the loss \spaces{7}.”


\newpage


1. Our Last end is to promote \answer{God's glory}  in  eternity.  
2.  We  shall  do  this
either in \answer{Heaven} or in \answer{Hell} according to our choice. 
3. Man's first  great
need is \answer{knowledge}.  
4.  In  heaven  God's  essence  is  known  by  the  blessed
(mediately) (\answer{immediately}). 
5. St. Paul says: “But then I shall know even  as
\answer{I am known}.” 
6. St. John says that in heaven we shall see God “even as  \answer{He is}.”
7. Only by the help of the \answer{Light of Glory} will our intellect be able  to  stand  the
beatific vision. 
8. Man's second great need is \answer{Love}. 
9. The  blessed  know
and love God to the full extent to which He is knowable and lovable.  (True)
(\answer{False}). 
10. They know Him in the way He knows Himself, and  they  love  Him
in the way He loves Himself. (\answer{True}) (False). 
11.  They  know  and  love  Him
infinitely. (True) (\answer{False}). 
12. Sharing His knowledge and  love,  they  must
share also His \answer{Happiness}. 
13. A  being  is  perfectly  happy  when  it  has  no
desires \answer{unfulfilled} forever. 
14. All our desires for sensible  delights  will  be
fully satisfied in heaven  after  \answer{the resurrection}.  
15.  The  beatific  vision  (can)
(\answer{cannot}) be lost by those in heaven. 
16. Heaven (\answer{is}) (is not)  eternal.  
17.
Some souls will be happier than others in heaven. (\answer{True})  (False).  
18.  The
degree of happiness will depend on \answer{merit, grace, charity}. 
19. Christ will invite  even  the
least of the blessed to “enter the joy  of  \answer{the Lord}.”  
20.  Heaven  is  often
called “eternal \answer{life}.” 
21. Hell was  first  made  to  punish  \answer{angels}.  
22.
Christ threatened with \answer{eternal damnation} those who refused to accept  His  truths.  
23.
On the Last Day, He will  say  to  the  lost:  “\answer{depart from me into everlasting fire}.”  
24.  This  is  the
sentence of  a  \answer{Judge};  hence  its  words  must  be  taken  in  a  (\answer{proper})
(figurative) sense. 
25. The main suffering in hell is the \answer{pain of loss}. 
26. It  is
made up of  four  different  sufferings,  namely  \answer{sadness},   \answer{loneliness},  \answer{contradiction},
\answer{annihilation}. 
27. Instead of hope, there is \answer{despair} in hell.  
28.  The  regret  of
the lost concerning sin is called \answer{remorse}, it (is) (\answer{is not}) true  contrition.
29. We (\answer{do}) (do not) admit the presence of material fire in hell. 
30.  Every
material thing can enable a spirit to be in a \answer{place}. 
31.  It  can  imprison
it there, if used as God's \answer{instrument}. 
32. The Church (\answer{has})  (has  not)  defined
that hell is eternal. 
33. A soul in hell (would) (\answer{would not}) come out if  it
were allowed to do so. 
34. In every mortal sin we choose  ourselves  instead
of God as our \answer{last end}. 
35. As far as our natural power goes, this  choice  is
\answer{irrevocable}. 
36. If we repent, it is due to \answer{grace}. 
37. God (can)  (\answer{cannot})  give
the grace of repentance to a soul in hell. 
38. Every  human  being  must  be
happy in eternity unless he deliberately chooses  to  be  otherwise.  (\answer{True})
(False). 
39. No one can go to hell except  through  his  own  fault.  (\answer{True})
(False). 
40. Christ says: “What doth it profit a man if he gain \answer{the whole world},  and
suffer the loss \answer{his soul}.”



\end{document}
