% This file was converted to LaTeX by Writer2LaTeX ver. 1.4
% see http://writer2latex.sourceforge.net for more info
\documentclass[a4paper,14pt]{memoir}
%\usepackage[ascii]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{libertine}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\newfontfamily\jarman{JARDOTTY}
\usepackage{color}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,nohead,nofoot]{geometry}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}
% Footnote rule
\setlength{\skip\footins}{0.119cm}
\renewcommand\footnoterule{\vspace*{-0.018cm}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.018cm}}\vspace*{0.101cm}}

\newcommand\textjarman[1]{{\jarman #1}}
\newcommand\answer[1]{\textbf{\textit{#1}}}
\newcounter{z}
\setcounter{z}{0}
\newcommand\spaces[1]{\rule{0pt}{18pt} \_\loop \ifnum\value{z} < #1
~\_%
\stepcounter{z}%
\repeat%
\setcounter{z}{0}}

\title{}
\begin{document}

\setlength{\parskip}{6pt plus2pt minus2pt}


\noindent Name:

\bigskip

~

\bigskip

\noindent {\Large Chapter LV -- The End of the World}

\bigskip

\bigskip


1. On the Last Day the world (\textjarman{will}) (\textjarman{will not}) be annihilated. 

2.  Scripture
says that it will be changed into “a \spaces{7} heavens and a \spaces{7} earth.”  

3.
Four signs of the end of the world are: 

\begin{itemize}
\item  \spaces{7},  
\item  \spaces{7},  
\item \spaces{7}, 
\item \spaces{7}.
\end{itemize} 


4.
The union between our body and soul is (\textjarman{a substantial}) (\textjarman{an accidental})  one.


5. It is broken at the moment of \spaces{7}. 

6. Its restoration  is  called  the
\spaces{7}. 

7. At the resurrection, each will receive (\textjarman{a body}) (\textjarman{his  own  body}).


8. Christ raised three human beings from the  dead,  namely  
\begin{itemize}
\item  \spaces{7},  
\item \spaces{7}, 
\item \spaces{7}.
\end{itemize} 

9. He also foretold His own \spaces{7}; and actually raised  Himself
from the dead. 

10. He said: “Destroy this \spaces{7}, and in three days  I  will
raise it up.” 

11. It  was  through  means  of  \spaces{7}  that  God  told  Mary
Madgalen that Christ had risen.  

\eject

12.  A  glorified  body  has  four  amazing
powers, namely, \begin{itemize}
\item \spaces{7},
\item  \spaces{7},  
\item \spaces{7}, 
\item \spaces{7}.
\end{itemize} 

13. St. Paul says of  the
body of the saved: 

\begin{quote}
“It is sown in \spaces{9} it shall  rise  in  \spaces{10}. \\ It  is
sown in \spaces{7}; it shall rise in \spaces{7}.\\ It is  sown  in  \spaces{7};  it  shall
rise in \spaces{7}.\\ It is sown a \spaces{7} body; it shall rise a \spaces{9} body.”  
\end{quote}

14.
“O death, where is thy \spaces{7}? O death, where is thy \spaces{7}”  

15.  Scripture
says that the bodies of the lost shall be  “salted  with  \spaces{7}.”  

16.  The
Last Judgement is necessary for us as (\textjarman{individuals}) (\textjarman{members of  the  race}).


17. Christ will be Judge as (\textjarman{God}) (\textjarman{Man}). 

18. He says that even  “every  idle
\spaces{7}” will be made known to all at the  Judgement.  The  sentence  at  the
Last Judgement will be (\textjarman{revocable}) (\textjarman{irrevocable}). 

19. Children destined  for
Limbo (\textjarman{will}) (\textjarman{will not}) be present at the Last Judgement. 

20.  To  be  ready
for the judgement, St. John tells us to “\spaces{7} in Him.”


\newpage



1. On the Last Day the world (\answer{will}) (will not) be annihilated. 
2.  Scripture
says that it will be changed into “a \answer{new} heavens and a \answer{new} earth.”  
3.
Four signs of the end of the world are: \answer{Gospel preached to all. Coming of Anti-Christ. Return of Elias. Conversion of the Jews.}
4.
The union between our body and soul is (\answer{a substantial}) (an accidental)  one.
5. It is broken at the moment of \answer{death}. 
6. Its restoration  is  called  the
\answer{resurrection}. 
7. At the resurrection, each will receive (a body) (\answer{his  own  body}).
8. Christ raised three human beings from the  dead,  namely  \answer{Lazarus},  \answer{the son of the widow of Naim}
and \answer{Jairus' daughter}. 
9. He also foretold His own \answer{death}; and actually raised  Himself
from the dead. 
10. He said: “Destroy this \answer{temple}, and in three days  I  will
raise it up.” 
11. It  was  through  means  of  \answer{an angel}  that  God  told  Mary
Madgalen that Christ had risen.  
12.  A  glorified  body  has  four  amazing
powers, namely, \answer{subtilty}, \answer{agility}, \answer{incorruptibility} and \answer{clarity}. 
13. St. Paul says of  the
body of the saved: “It is sown in \answer{corruption} it shall  rise  in  \answer{incorruption}.  It  is
sown in \answer{dishonour}; it shall rise in \answer{glory}. It is  sown  in  \answer{weakness};  it  shall
rise in \answer{power}. It is sown a \answer{natural} body; it shall rise a \answer{supernatural} body.”  
14.
“O death, where is thy \answer{victory}? O death, where is thy \answer{sting}”  
15.  Scripture
says that the bodies of the lost shall be  “salted  with  \answer{fire}.”  
16.  The
Last Judgement is necessary for us as (individuals) (\answer{members of  the  race}).
17. Christ will be Judge as (God) (\answer{Man}). 
18. He says that even  ``every  idle
\answer{word}'' will be made known to all at the  Judgement.  The  sentence  at  the
Last Judgement will be (revocable) (\answer{irrevocable}). 
19. Children destined  for
Limbo (\answer{will}) (will not) be present at the Last Judgement.
20.  To  be  ready
for the judgement, St. John tells us to “\answer{abide} in Him.”


\end{document}
